\subsubsection*{Written by People Who Code}

{\itshape  Cindy Chen, Parth Oza, Jagan Prem, Kevin Shen }

\subsection*{What is Track\+It?}

Track\+It is a package tracking software written by People Who Code, a developer team consisting of the members Cindy Chen, Parth Oza, Jagan Prem, and Kevin Shen, for the I\+DT Programming Contest. ​  \subsection*{Overview}

Track\+It is an easy-\/to-\/use website that allows users to track their packages as they are being delivered. Users can enter their Package U\+U\+I\+Ds one-\/by-\/one to see more detailed information on them, while admins can see a list of all packages currently being delivered. ​ \subsection*{User Mode}

\subsubsection*{Map}

 The map is a visual display of the packages. It shows where each entered package originated and where it is. ​ \subsubsection*{Enter U\+U\+ID}

Here, users can enter the U\+U\+ID of packages they want to track, and click \char`\"{}\+Add\char`\"{} to add the package to the tracking list.  \subsubsection*{Package List}

This is a list of entered packages. Users can click the 4 buttons at the top for quick selection and deselection of packages (for showing on the map), or they can check/uncheck the checkboxes at the left of each package. The shown color of each package on the map can also be changed by clicking the colored squares. You can also click the row to expand it, viewing more detailed information. It can be clicked again to collapse it.  ​ \subsection*{Admin Mode}

Admin mode is a feature for administrators to track all packages at once. Although many of its features remain the same as in user mode, there are a few differences. ​ \subsubsection*{Logging In}

To log in to admin mode, simply go to the top and click \char`\"{}\+Log In.\char`\"{}  \subsubsection*{New Toolbar}

In admin mode, there are a few new options in the top bar.  These new buttons allow admins to add all delivered/undelivered packages to the tracking list. Through this and the other tools in the tracking list, it is easy for an admin to look at only the packages they want to see. Once the administrator is done, he/she can log out. ​ \subsubsection*{All Packages}

All packages can be viewed when both buttons at the top are clicked.  