\hypertarget{namespacetime__shifter}{}\section{time\+\_\+shifter Namespace Reference}
\label{namespacetime__shifter}\index{time\+\_\+shifter@{time\+\_\+shifter}}
\subsection*{Variables}


\subsection{Variable Documentation}
\index{time\+\_\+shifter@{time\+\_\+shifter}!change@{change}}
\index{change@{change}!time\+\_\+shifter@{time\+\_\+shifter}}
\subsubsection[{\texorpdfstring{change}{change}}]{\setlength{\rightskip}{0pt plus 5cm}int change = {\bf now}-\/gpx.\+tracks\mbox{[}0\mbox{]}.segments\mbox{[}0\mbox{]}.points\mbox{[}0\mbox{]}.time.\+timestamp()+6000}\hypertarget{namespacetime__shifter_ac710c7bfde8686dcdfa07f1800ab01b5}{}\label{namespacetime__shifter_ac710c7bfde8686dcdfa07f1800ab01b5}


The seconds needed to shift the G\+PX\textquotesingle{}s time to now. 



Definition at line 13 of file time\+\_\+shifter.\+py.

\index{time\+\_\+shifter@{time\+\_\+shifter}!delta@{delta}}
\index{delta@{delta}!time\+\_\+shifter@{time\+\_\+shifter}}
\subsubsection[{\texorpdfstring{delta}{delta}}]{\setlength{\rightskip}{0pt plus 5cm}delta = datetime.\+timedelta(0, {\bf change}, 0)}\hypertarget{namespacetime__shifter_a66db7c5e4e9699c54207ab857ae72cb7}{}\label{namespacetime__shifter_a66db7c5e4e9699c54207ab857ae72cb7}


The shift represented as a datetime.\+timedelta. 



Definition at line 15 of file time\+\_\+shifter.\+py.

\index{time\+\_\+shifter@{time\+\_\+shifter}!file@{file}}
\index{file@{file}!time\+\_\+shifter@{time\+\_\+shifter}}
\subsubsection[{\texorpdfstring{file}{file}}]{\setlength{\rightskip}{0pt plus 5cm}file = open(F\+I\+L\+E\+\_\+\+N\+A\+ME, \char`\"{}w\char`\"{})}\hypertarget{namespacetime__shifter_a40a5d58ffa6e88aa578d6683ac413105}{}\label{namespacetime__shifter_a40a5d58ffa6e88aa578d6683ac413105}


The G\+PX that is being shifted. 



Definition at line 22 of file time\+\_\+shifter.\+py.

\index{time\+\_\+shifter@{time\+\_\+shifter}!gpx@{gpx}}
\index{gpx@{gpx}!time\+\_\+shifter@{time\+\_\+shifter}}
\subsubsection[{\texorpdfstring{gpx}{gpx}}]{\setlength{\rightskip}{0pt plus 5cm}gpx = gpxpy.\+parse(open(F\+I\+L\+E\+\_\+\+N\+A\+ME))}\hypertarget{namespacetime__shifter_a701030976c24adaa37c6bbf9af499ac8}{}\label{namespacetime__shifter_a701030976c24adaa37c6bbf9af499ac8}


The G\+PX object created from the G\+PX file data. 



Definition at line 9 of file time\+\_\+shifter.\+py.

\index{time\+\_\+shifter@{time\+\_\+shifter}!now@{now}}
\index{now@{now}!time\+\_\+shifter@{time\+\_\+shifter}}
\subsubsection[{\texorpdfstring{now}{now}}]{\setlength{\rightskip}{0pt plus 5cm}now = time.\+time()}\hypertarget{namespacetime__shifter_afdc24ca189ea1f66dfd9245b4c970d59}{}\label{namespacetime__shifter_afdc24ca189ea1f66dfd9245b4c970d59}


The current time in seconds from epoch. 



Definition at line 11 of file time\+\_\+shifter.\+py.

\index{time\+\_\+shifter@{time\+\_\+shifter}!temp\+\_\+text@{temp\+\_\+text}}
\index{temp\+\_\+text@{temp\+\_\+text}!time\+\_\+shifter@{time\+\_\+shifter}}
\subsubsection[{\texorpdfstring{temp\+\_\+text}{temp_text}}]{\setlength{\rightskip}{0pt plus 5cm}temp\+\_\+text = gpx.\+to\+\_\+xml()}\hypertarget{namespacetime__shifter_acfe3ecceec8adb15641afbf1805061dc}{}\label{namespacetime__shifter_acfe3ecceec8adb15641afbf1805061dc}


The time-\/shifted data for the G\+PX file. 



Definition at line 18 of file time\+\_\+shifter.\+py.

